A Dearth of Young Stars and Planets in the Kepler Field

### 2024-05-27 paper/ms.tex
update ms

	\vspace{-0.35cm}
    \subfloat{
%    \includegraphics[width=.96\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000_preciseagesonly.pdf}
    \includegraphics[width=.96\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240521_maxage4000_preciseagesonly.pdf}
    }
  \end{center}
  \vspace{-0.66cm}
  \caption{{\bf Kepler's demographic cliff,} visible in the
  rotation-derived ages of stars (left) and planet hosts (middle) in
  the Kepler field.  The top row corresponds to all stars with
  temperatures of 3800--6200\,K for which we calculated rotation-based
  ages.  The opaque lines impose quality cuts on factors such as
  binarity, crowding, and the star's evolutionary state.  The bottom
  row selects only stars with temperatures of 4400-5400\,K, which have
  relatively precise ages near 2\,Gyr due to their fast spin-down.
  The statistical uncertainty for a mean
  individual star at 1, 2, and 3\,Gyr is shown, and is identical
  across each row.  Finally, the right panel compares the
  rotation-derived ages against star formation histories
  derived using CMD fitting.  Completeness in Kepler's
  $P$$_{\rm rot}$ detection sensitivity is near unity until
  $t$$\lesssim$3\,Gyr \citep{2022ApJ...937...94M}.
  \label{fig:hist_tgyro}
  }
\end{figure*}

@@

The age distributions of Kepler stars and planet hosts are
nearly indistinguishable.  A simple diagnostic of whether the two
distributions are drawn from the same underlying distribution is the
Kolmogorov-Smirnov test;  we calculated this statistic in a manner
that accounts for the Poisson uncertainties by performing 100 random
draws of 70\% of the stars from each sample.  The resulting median
$p$-values were $\approx$0.01 for both rows of
Figure~\ref{fig:hist_tgyro}.  This degree of similarity suggests that
the ``common wisdom'' that young transiting planets are hard to detect
because their host stars are photometrically variable requires some
nuance.  If true, this statement only holds for the very youngest
stars, since at the age resolution of this study, there appears to be
little to no selection bias against sub-gigayear planets.

@@

\software{
  astropy \citep{Astropy18},
  matplotlib \citep{matplotlib},
  numpy \citep{numpy},
  scipy \citep{scipy},
}

>>>>

	\vspace{-0.35cm}
    \subfloat{
%    \includegraphics[width=.96\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000_preciseagesonly.pdf}
    \includegraphics[width=.96\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240521_maxage4000_preciseagesonly.pdf}
    }
  \end{center}
  \vspace{-0.66cm}
  \caption{{\bf Kepler's demographic cliff,} visible in the
  rotation-derived ages of stars (left) and planet hosts (middle) in
  the Kepler field.  The top row shows all stars with
  temperatures of 3800--6200\,K for which we calculated rotation-based
  ages.  Opaque lines impose quality cuts on 
  binarity, crowding, and the star's evolutionary state; transparent lines do not.
  The bottom
  shows stars with temperatures of 4400--5400\,K, which have
  more precise ages due to their fast spin-down.
  The statistical uncertainty for a mean
  individual star at 1, 2, and 3\,Gyr is shown, and is identical
  across each row.  Finally, the right panel compares the
  rotation-derived ages against star formation histories
  derived using CMD fitting (dashed and dotted lines).  Completeness in Kepler's
  $P$$_{\rm rot}$ detection sensitivity is near unity until
  $t$$\lesssim$3\,Gyr \citep{2022ApJ...937...94M}.
  \label{fig:hist_tgyro}
  }
\end{figure*}

@@

The age distributions of Kepler stars and planet hosts are quite
similar.  A simple diagnostic of whether the two
distributions are drawn from the same underlying distribution is the
Kolmogorov-Smirnov test;  we calculated this statistic in a manner
that accounts for the Poisson uncertainties by performing 1000 random
draws of 70\% of the stars from each sample.  The resulting 
range of $\log_{\rm 10}p$-values (2.5$^{\rm th}$ to 97.5$^{\rm th}$ percentile)
spanned -3.9 to -1.2 for the K-dwarfs only,
and -5.2 to -2.2 for all Kepler stars.  This degree of similarity suggests that
the ``common wisdom'' that young transiting planets are hard to detect
because their host stars are photometrically variable requires some
nuance.  If true, this statement only holds for the very youngest
stars, since at the age resolution of this study, there appears to be
little to no selection bias against sub-gigayear planets.

@@

\software{
  astropy \citep{Astropy18},
  claude \citep{claude2024anthropic},
  matplotlib \citep{matplotlib},
  numpy \citep{numpy},
  scipy \citep{scipy},
}
